\documentclass[12pt]{article}
\usepackage{intentspec}
\begin{document}
\section{Jam Example}

This is an example for testing new formatting for intent specifications.
Features include:

\begin{enumerate}
\item macros for citing and linking to another ``iitem'' with an arrow
\item modification of the enumeration environment to include a specified prefix
\item an ``intent item'' (iitem) macro to include four parameters:
  \begin {enumerate}
  \item a label to be used when citing this item elsewhere in the document
  \item a short description (which appears in bold)
  \item a longer description of the item
    \item a place to cite other related intent items
  \end{enumerate}
\end{enumerate}

I have included a margin note as an example of how, when writing intent specifications, I have left commentary for subsequent editing passes.

\subsection{System Goals}
\begin{intent}{Goal}{G}
  \iitem{g:preserves}{preserves}{Turn berries into jam.\marginpar{$\leftarrow$ Observe sub-levels from nested ``enumerate'' environment.}}{\downtrace{l:mission}}
  \begin{enumerate}
    \iitem{g:stone}{stone fruit}{
      \begin{enumerate}
      \item peach
      \item cherry
      \item plum
      \end{enumerate}
      Include these preserves, even though stone fruit is not a berry.}{}
    \iitem{g:blueberry}{blueberry}{Blueberry should be among the initial offerings.}{}
    \iitem{g:raspberry}{raspberry}{}{}
    \end{enumerate}
  \begin{assumption}Citrus is a hesperidium, not a berry, and can only be made into marmelade, not into jam.\end{assumption}
  \iitem{g:preserve}{preservation}{Do no harm to the other existing systems.}{\downtrace{l:interfere}, \downtrace{l:equip}}\marginpar{$\leftarrow$ This seems like more of a loss.}
  \begin{assumption}Vishnu the Preserver will assist.\end{assumption}
  \iitem{g:pre-serve}{pre-serve}{Flatter the MVPs by serving sneak-preview jam.}{}
\end{intent}

\subsection{Losses}
\begin{intent}{Loss}{L}
  \iitem{l:equip}{equipment damage}{Damage or destroy equipment in the course of cooking.}{\uptrace{g:preserve}}
  \iitem{l:interfere}{kitchen interference}{Interfere with the cooking of other food.}{\uptrace{g:preserve}}
  \iitem{l:mission}{mission loss}{Fail to produce a sufficient quantity of jam of sufficient quality.}{\uptrace{g:preserves}}
  \iitem{l:life}{life and limb}{Injury or death of someone in the jam-production facility or a consumer of the jam.}{}
  \end{intent}


\end{document}
